Supplementary material to: Drug efficacy prediction in cell lines

### 2019-05-21 docs/manuscript1.Rnw

  \section{General model}
  In addition to the outcome co-data $\mathbf{c}_d$, we may have feature co-data
  $\mathbf{z}_j$ available. Examples of this in omics settings are pathway 
  memberships or previously obtained $p$-values for the features. In
  that case, we extend model (\ref{eq:priormodel}) to:
  \begin{subequations}\label{eq:generalmodel}
    \begin{align}
      y_{id} | \bm{\beta}_d, \sigma_d^2 & \sim \mathcal{N} 
      (\x_i \tr \bm{\beta}_d, \sigma_d^2), \nonumber \\
      \beta_{jd} | \tau_j^2, \gamma_d^2, \sigma_d^2 & \sim \mathcal{N} 
      (0, \sigma_d^2 \gamma_d^2 \tau_j^2), \\
      \gamma_d^2 & \sim \mathcal{IG}\(\theta_d^c, \lambda^c_d\), \\
      \tau_j^2 & \sim \mathcal{IG}\(\theta_j^z, \lambda^z_j\), \\
      \sigma_d^2 & \sim 1/\sigma_d^3, \nonumber
    \end{align}
  \end{subequations}
  where we now have an extra variance component $\tau_j$ that is 
  \textit{a priori} inverse Gaussian distributed with mean dependent on the 
  feature co-data $\mathbf{z}_j$. Equivalently, we may set 
  $\eta_{jd}^2=\tau_j^2 \gamma_d^2/(\theta_j^z \theta_d^c)$ and write 
  (\ref{eq:generalmodel}) as:
  \begin{align*}
    \beta_{jd} | \eta_{jd}^2, \sigma_d^2 & \sim \mathcal{N} 
    \(0, \frac{\lambda_{jd}}{\chi_{jd}}\eta_{jd}^2\sigma_d^2\), \\
    \eta_{jd}^2 & \overset{D}{=}\pi^{-1}\sqrt{\chi_{jd}}\exp(\psi_{jd}) 
    \eta_{jd}^{-3/2} \cdot K_{0} \(\sqrt{\psi_{jd}^2 + \chi_{jd} (\eta_{jd}^2 
    + \eta_{jd}^{-2} - 2)} \),
  \end{align*}
  where $\lambda_{jd}=\lambda_j^z\lambda_d^c$, 
  $\chi_{jd}=\lambda_j^z\lambda_d^c/(\theta_j^z \theta_d^c)$, and
  $\psi_{jd}=\lambda_j^z/\theta_j^z + \lambda_d^c/ \theta_d^c$. A third way
  of writing the model is:
  \begin{subequations}\label{eq:generalprior}
    \begin{align}
      \beta_{jd} | \eta_{jd}^2, \sigma_d^2 & \sim \mathcal{N} 
      \(0, \eta_{jd}^2 \sigma_d^2\), \\
      \eta_{jd}^2 | \xi_{d}^2 & \sim \mathcal{IG} 
      (\theta_j^z \xi_d^2, \lambda_j^z \xi_d^2 ), \\
      \xi_d^2 & \sim \mathcal{GIG} (1, \lambda_d^c/(\theta_d^c)^2, \lambda_d^c).
    \end{align}
  \end{subequations}
  From (\ref{eq:generalprior}) we find the marginal variance and kurtosis for 
  $\beta_{jd}$ (conditional on $\sigma_d^2$):
  \begin{align}
    \V(\beta_{jd} | \sigma_d^2) & =\sigma_d^2 \theta_j^z \theta_d^c 
    \[\frac{K_0(\lambda_d^c/\theta_d^c)}{K_1(\lambda_d^c/\theta_d^c)} + 
    \frac{2\theta_d^c}{\lambda_d^c}\],\nonumber \\
    \mathcal{K}(\beta_{jd} | \sigma_d^2) & = 3 \(\frac{\theta_j^z}{\lambda_j^z}
    + 1\) \theta_d^c \[r_d - r_d^{-1} + 8\(\frac{\theta_d^c}{\lambda_d^c}\)^2
    K_0 (\lambda_d^c/\theta_d^c) + \frac{4 \theta_d^c}{\lambda_d^c}r_d 
    K_0 (\lambda_d^c/\theta_d^c) + 1/\theta_d^c\], \label{eq:kurtnigig}
  \end{align}
  with $r_d = K_0(\lambda_d^c/\theta_d^c)/K_1(\lambda_d^c/\theta_d^c)$. If 
  we fix the prior expectation $\E(\gamma_d^2)=\theta_d^c$ and let the prior 
  variance 
  $\V(\gamma_d^2)$ go to zero, we have $\V(\beta_{jd} | \sigma_d^2) \rightarrow
  \sigma_d^2 \theta_j^z \theta_d^c$ and $\mathcal{K}(\beta_{jd} | \sigma_d^2)
  \rightarrow 3(\theta_j^z/\lambda_j^z + 1)$. From (\ref{eq:kurtnigig}) we see
  that we can keep the variance constant by fixing $\theta_j^z$, $\theta_d^c$,
  and $\lambda_d^c$, while we increasing the kurtosis by decrearing 
  $\lambda_j^z$. This makes the model (\ref{eq:generalmodel}), which we 
  refer to by the NIGIG model hereafter, a flexible model.

@@

  \section{Simulations}
  \subsection{Comparison of NIG and Student's \texorpdfstring{$t$}{t} priors}
  \label{sec:inversegammamodel}
  A common default prior for latent variance components is the inverse Gamma
  prior:
  $$
  \gamma_d^2 \sim \Gamma^{-1}(\eta_d/2,\lambda_d/2),
  $$
  with shape $\eta_d/2$ and scale $\lambda_d/2$, both rescaled to match our 
  inverse Gaussian prior formulation. The resulting marginal prior for the model
  parameters
  (conditional on the error variance $\sigma_d^2$) is then a scaled Student's 
  $t$-distribution:
  $$
  \beta_j | \sigma_d^2 \sim \text{Student's } 
  t\(\eta_d,\sigma_d \sqrt{\lambda_d/\eta_d}\),
  $$
  with degrees of freedom $\eta_d$ and scale $\sigma_d \sqrt{\lambda_d/\eta_d}$.
  See SM Section \ref{sm-sec:inversegamma} for more details on this prior. 
  We compare the 
  posteriors of the proposed NIG prior and the scaled Student's $t$-distribution
  prior in a simulated setting.

  We compare the two posterior distributions to the true posterior for a 
  number of measures. Divergence between the distributions
  is quantified through a multivariate extension of the Cram{\'e}r-von Mises
  criterion \cite[]{baringhaus_new_2004}, where smaller values of the criterion
  indicate more similar distributions. We also assess 95\% coverage of the 
  posterior credible intervals. The accuracy of the 
  point estimates of $\beta_j$ in the form of posterior means is assessed by
  the mean squared distance (MSD) and correlation between the point estimates 
  and the true $\beta_j$.

  The aim of this simulation study is to investigate the performance of the NIG 
  prior model, so we set $D=1$ and drop the $d$ indices in the following. 
  We studied two settings: one dense and one sparse. In the dense setting, 
  we simulated $n=100$ features $\x_i$ from a $p=200$ dimensional Gaussian 
  distribution with zero mean vector, variances equal to one, and all 
  covariances set to $\rho=0.5$. The outcomes were generated through $y_i = 
  \x_i\tr \bbeta + \epsilon_i$, with the $\epsilon_i$ from the standard normal 
  distribution. 
  Likewise, we generated the model parameters $\beta_j$ from a standard normal
  distribution. For estimation, we set our hyperparameters $\lambda=0.5$, 
  $\theta=1$, and $\eta=2.5$. such that the marginal $\beta_j$ variances
  of the NIG and Student's $t$ priors match. For both priors, we generated 
  1000 draws (after 1000 burnin) from the posteriors using an MCMC sampler 
  implemented in \texttt{rstan}.

  In the sparse setting, the observed data generating process is the same. The
  model parameters are are simulated from a spike-and-slab prior with a 
  Laplace slab:
  \begin{align*}
    w & \sim \text{Beta}(\nu, \kappa), \\
    z_j | w & \sim \text{Binom}(w), \\
    \beta_j | z_j & \sim z_j\text{Laplace}
    \(\sqrt{\frac{\nu + \kappa}{2\nu}} \sigma \gamma\) + (1 - z_j)\delta_0,
  \end{align*}
  where $\delta_0$ denotes the Dirac mass at zero. The Laplace scale is chosen
  such that the we have marginal prior variance $\V(\beta_j)=1$. The sparsity 
  level is determined by the proportion of zero $\beta_j$, 
  $s=1 - \nu/(\nu + \kappa)$. Note that the resulting marginal prior for
  $\beta_j$ is:
  $$
  \beta_j \sim (s - 1)\text{Laplace}\(\sqrt{\frac{\nu + \kappa}{2\nu}} 
  \sigma \gamma\) + s\delta_0.
  $$
  We use two settings, $s=0.5$ and $s=0.9$. The 
  hyperparameters for estimation are set the same as in the dense setting.
  To mitigate the effect of random variation, we
  repeated the simulations 100 times and report the results in Figures 
  \ref{fig:boxplots_igaussian_res4_post} and [! ref to figure here]
<<boxplots_igaussian_res4_post, fig.cap="Comparison of the NIG and Student's t priors through (a) Cramér-von Mises criterion between the model and true posteriors, (b) correlation and (c) MSD between the posterior means and true parameters, and (d) 95\\% credible interval coverage of the true values.", out.width="100%", fig.asp=2/5>>=
@

@@

@@

  \section{Discussion}
  - inverse Gaussian more convenient than inverse Gamma, because EB is closed-
  form

>>>>

  \section{General model}
  In addition to the outcome co-data $\mathbf{c}_d$, we may have feature co-data
  $\mathbf{z}_j$ available. Examples of this in omics settings are pathway 
  memberships or previously obtained $p$-values for the features. In
  that case, we extend model (\ref{eq:priormodel}) to:
  \begin{subequations}\label{eq:generalmodel}
    \begin{align}
      y_{id} | \bm{\beta}_d, \sigma_d^2 & \sim \mathcal{N} 
      (\x_i \tr \bm{\beta}_d, \sigma_d^2), \nonumber \\
      \beta_{jd} | \tau_j^2, \gamma_d^2, \sigma_d^2 & \sim \mathcal{N} 
      (0, \sigma_d^2 \gamma_d^2 \tau_j^2), \\
      \gamma_d^2 & \sim \mathcal{IG}\(\theta_d^c, \lambda^c_d\), \\
      \tau_j^2 & \sim \mathcal{IG}\(\theta_j^z, \lambda^z_j\), \\
      \sigma_d^2 & \sim 1/\sigma_d^3, \nonumber
    \end{align}
  \end{subequations}
  where we now have an extra variance component $\tau_j$ that is 
  \textit{a priori} inverse Gaussian distributed with mean dependent on the 
  feature co-data $\mathbf{z}_j$. We will refer to this model as the normal
  inverse Gaussian-inverse Gaussian (NIGIG) model. See SM Section 
  \ref{sm-sec:nigigprior} for more details on this prior.

@@

  \section{Simulations}
  \subsection{Comparison of NIG, NIGIG and Student's \texorpdfstring{$t$}{t} 
  priors}
  \label{sec:inversegammamodel}
  A common default prior for latent variance components is the inverse Gamma
  prior:
  $$
  \gamma_d^2 \sim \Gamma^{-1}(\eta_d/2,\lambda_d/2),
  $$
  with shape $\eta_d/2$ and scale $\lambda_d/2$, both rescaled to match our 
  inverse Gaussian prior formulation. The resulting marginal prior for the model
  parameters
  (conditional on the error variance $\sigma_d^2$) is then a scaled Student's 
  $t$-distribution:
  $$
  \beta_j | \sigma_d^2 \sim \text{Student's } 
  t\(\eta_d,\sigma_d \sqrt{\lambda_d/\eta_d}\),
  $$
  with degrees of freedom $\eta_d$ and scale $\sigma_d \sqrt{\lambda_d/\eta_d}$.
  See SM Section \ref{sm-sec:inversegamma} for more details on this prior. 
  We compare the 
  posteriors of the proposed NIG and NIGIG priors to the scaled Student's 
  $t$-distribution prior in a simulated setting.

  We compare the three posterior distributions to the true posterior for a 
  number of measures. Divergence between the distributions
  is quantified through a multivariate extension of the Cram{\'e}r-von Mises
  criterion \cite[]{baringhaus_new_2004}, where smaller values of the criterion
  indicate more similar distributions. We also assess 95\% coverage of the 
  posterior credible intervals. The accuracy of the 
  point estimates of $\beta_j$ in the form of posterior means is assessed by
  the mean squared distance (MSD) and correlation between the point estimates 
  and the true $\beta_j$.

  The aim of this simulation study is to investigate the performance of the NIG 
  prior model, so we set $D=1$ and drop the $d$ indices in the following. 
  We studied two settings: one dense and one sparse. In the dense setting, 
  we simulated $n=100$ features $\x_i$ from a $p=200$ dimensional Gaussian 
  distribution with zero mean vector, variances equal to one, and all 
  covariances set to $\rho=0.5$. The outcomes were generated through $y_i = 
  \x_i\tr \bbeta + \epsilon_i$, with the $\epsilon_i$ from the standard normal 
  distribution. 
  Likewise, we generated the model parameters $\beta_j$ from a standard normal
  distribution.

  We choose the hyperparameters such that we get all combinations of marginal
  prior variances and kurtoses $\V(\beta_{jd} | \sigma_d^2) \in 
  \{ 1/2, 1, 2 \}$ and $\mathcal{K}(\beta_{jd} | \sigma_d^2) \in 
  \{ 4, 10 \}$. This leads to the settings in Table \ref{tab:hyper_set1}. For 
  all priors, we generated 1000 draws (after 1000 burnin) from the 
  posteriors using an MCMC sampler implemented in \texttt{rstan}. We repeated
  the simulations 100 times and report 
  results in Figures \ref{fig:boxplots_igaussian_res4_post1} and 
  \ref{fig:boxplots_igaussian_res4_post2}. 
<<hyper_set1>>= 
set <- read.table("results/simulations_igaussian_set4.csv")
kableExtra::kable_styling(
  knitr::kable(set[, c("lambdac", "thetac", "lambdaz", "thetaz",
                       "eta", "lambda", "vars", "kurts")], 
               col.names=c("$\\lambda^c$", "$\\theta^c$", "$\\lambda^z$",
                           "$\\theta^z$", "$\\eta$", "$\\lambda$", 
                           "$\\V(\\beta_{jd} | \\sigma_d^2)$",
                           "$\\mathcal{K}(\\beta_{jd} | \\sigma_d^2)$"), 
               caption="Hyperparameter settings", 
               "latex", booktabs=TRUE, escape=FALSE, digits=2),
  latex_options=c("HOLD_position"))
@

  <<boxplots_igaussian_res4_post1, fig.cap="Comparison of the NIG, NIGIG, and Student's t priors in (a)-(d) simulation setting 1, (e)-(h) setting 2, and (i)-(l) setting 3, through Cramér-von Mises criterion between the model and true posteriors, correlation and MSD between the posterior means and true parameters, and 95\\% credible interval coverage of the true values.", out.width="100%", fig.asp=1>>=
@

<<boxplots_igaussian_res4_post2, fig.cap="Comparison of the NIG, NIGIG, and Student's t priors in (a)-(d) simulation setting 4, (e)-(h) setting 5, and (i)-(l) setting 6, through Cramér-von Mises criterion between the model and true posteriors, correlation and MSD between the posterior means and true parameters, and 95\\% credible interval coverage of the true values.", out.width="100%", fig.asp=1>>=
@

@@

  In the sparse setting, the observed data generating process is the same. The
  model parameters are are simulated from a spike-and-slab prior with a 
  Gaussian slab:
  \begin{align*}
    w & \sim \text{Beta}(\nu, \kappa), \\
    z_j | w & \sim \text{Binom}(w), \\
    \beta_j | z_j & \sim z_j \mathcal{N} \( 0, 1\) +
    (1 - z_j)\delta_0,
  \end{align*}
  where $\delta_0$ denotes the Dirac mass at zero. The slab is chosen
  such that the we have marginal prior variance $\V(\beta_j)=1$. The sparsity 
  level is determined by the proportion of zero $\beta_j$, 
  $s=1 - \nu/(\nu + \kappa)$. Note that the resulting marginal prior for
  $\beta_j$ is:
  $$
  \beta_j \sim (s - 1)\mathcal{N} \( 0, 1\) + s\delta_0.
  $$
  We use two settings, $s=0.5$ and $s=0.9$. The 
  hyperparameters for estimation are set the same as in the dense setting, 
  resulting in a total of 12 different simulation settings.
  To mitigate the effect of random variation, we
  repeated the simulations 100 times and report the results in Figures 
  [! ref to figure here]

@@

  - metabolomics data: oxidative stress als uitkomst van de andere metabolieten
  min organic acids omdat ze downstream zijn. oxidateve stress onderverdelen in
  high and low als uitkomst co-data en de andere metabolieten onderverdelen
  als predictor co-data.
  \section{Discussion}
  - inverse Gaussian more convenient than inverse Gamma, because EB is closed-
  form

### 2019-05-21 docs/supplement2.Rnw

  \cite{moran_variance_2018} argue that in regression models, $\bm{\beta}_d$ and $\sigma_d^2$ should be independent \textit{a priori}. However, in our case that is debatable. The $D$ regressions need not be on the same scale, so some form of calibration of the $\bm{\beta}_d$ posteriors to this scale is required. A simple way of doing this is to include the scales $\sigma_d^2$ in the priors for the $\bm{\beta}_d$. We call the two versions of the model conjugate (with $\bm{\beta}_d$ and $\sigma_d^2$ dependent):
  $$
  \beta_{jd} | \gamma_d^2, \sigma_d^2 \sim \mathcal{N} (0, \sigma_d^2 \gamma_d^2)
  $$
  and non-conjugate (with $\bm{\beta}_d$ and $\sigma_d^2$ independent):
  $$
  \beta_{jd} | \gamma_d^2, \sigma_d^2 \sim \beta_{jd} | \gamma_d^2 \sim \mathcal{N} (0, \gamma_d^2),
  $$
  and compare them in our simulations.

	In addition to the inverse Gaussian model for the prior variances $\gamma_d^2$ (introduced in the MD):
	$$
  \gamma_d^2 \sim \mathcal{IG}(\theta_d, \lambda_d),
  $$
	we investigate a generalisation of the models in \cite{kpogbezan_empirical_2017} and \cite{leday_gene_2017}, where we draw the $\gamma_d^2$ from an inverse Gamma distribution; :
	$$
	\gamma_d^2 \sim \Gamma^{-1}(\eta_d/2, \lambda_d/2).
	$$
	For the sake of comparability, we have rescaled the inverse Gamma parameters and reparametrised both distributions as generalized inverse Gaussians:
	\begin{align*}
  \gamma_d^2 & \sim \mathcal{GIG}(-1/2, \lambda_d \theta_d^{-2}, \lambda_d), \\
  \gamma_d^2 & \sim \mathcal{GIG}(-\eta_d/2, 0, \lambda_d).
  \end{align*}
	The two models coincide if $\theta_d \to \infty$ and $\eta_d = 1$.

>>>>

  \cite{moran_variance_2018} argue that in regression models, $\bm{\beta}_d$ and $\sigma_d^2$ should be independent \textit{a priori}. However, in our case that is debatable. The $D$ regressions need not be on the same scale, so some form of calibration of the $\bm{\beta}_d$ posteriors to this scale is required. A simple way of doing this is to include the scales $\sigma_d^2$ in the priors for the $\bm{\beta}_d$. We call the two versions of the model conjugate (with $\bm{\beta}_d$ and $\sigma_d^2$ dependent \textit{a priori}):
  $$
  \beta_{jd} | \gamma_d^2, \sigma_d^2 \sim \mathcal{N} (0, \sigma_d^2 \gamma_d^2)
  $$
  and non-conjugate (with $\bm{\beta}_d$ and $\sigma_d^2$ independent \textit{a priori}):
  $$
  \beta_{jd} | \gamma_d^2, \sigma_d^2 \sim \beta_{jd} | \gamma_d^2 \sim \mathcal{N} (0, \gamma_d^2),
  $$
  and compare them in our simulations.

	In addition to the inverse Gaussian model for the prior variances $\gamma_d^2$ (introduced in the MD):
	$$
  \gamma_d^2 \sim \mathcal{IG}(\theta_d, \lambda_d),
  $$
	we investigate a generalisation of the models in \cite{kpogbezan_empirical_2017} and \cite{leday_gene_2017}, where we draw the $\gamma_d^2$ from an inverse Gamma distribution:
	$$
	\gamma_d^2 \sim \Gamma^{-1}(\eta_d/2, \lambda_d/2),
	$$
	with shape $\eta_d/2$ and scale $\lambda/2$. For the sake of comparability, we
	have rescaled the inverse Gamma parameters and reparametrised both 
	distributions as generalized inverse Gaussians:
	\begin{align*}
  \gamma_d^2 & \sim \mathcal{GIG}(-1/2, \lambda_d \theta_d^{-2}, \lambda_d), \\
  \gamma_d^2 & \sim \mathcal{GIG}(-\eta_d/2, 0, \lambda_d).
  \end{align*}
	The two models coincide if $\theta_d \to \infty$ and $\eta_d = 1$.

<<dens_igaussian_igamma, fig.cap="Several densities of the inverse Gaussian and inverse Gamma families", out.width="100%", fig.asp=2/3>>=
digauss <- function(x, theta, lambda, eta) {
  sqrt(lambda/(x^3*2*pi))*exp(-lambda*(x - theta)^2/(2*theta^2*x))
}

digamma <- function(x, theta, lambda, eta) {
  alpha <- eta/2
  beta <- lambda/2
  beta^alpha/gamma(alpha)*x^(-alpha - 1)*exp(-beta/x)
}

eta <- c(1, 2, 1, 1, 5)
lambda <- c(1, 1, 2, 1/2, 2)
theta <- c(1000, 1000, 1, 1, 1)

labels <- c("inv. Gaussian", "inv. Gamma")
col <- c(1, 2)

opar <- par(no.readonly=TRUE)
par(mar=opar$mar*c(1, 1.3, 1, 1))
layout(matrix(c(rep(c(1, 1, 2, 2, 3, 3), 2), rep(c(0, 4, 4, 5, 5, 0), 2)),
                 nrow=4, ncol=6, byrow=TRUE))
for(i in 1:length(eta)) {
  modes <- c(theta[i]*(sqrt(1 + 9*theta[i]^2/
                            (4*lambda[i]^2)) - 3*theta[i]/(2*lambda[i])),
             lambda[i]/(eta[i] + 2))
  ylim <- c(0, max(digauss(modes[1], theta[i], lambda[i], eta[i]),
                   digamma(modes[2], theta[i], lambda[i], eta[i])))
  curve(digauss(x, theta[i], lambda[i], eta[i]), 0.001, 5, n=1000,
        ylim=ylim, ylab="Density", "x", col=col[1], 
        main=bquote(eta==.(eta[i])*","~lambda==.(lambda[i])*","~theta==.(
          theta[i])))
  curve(digamma(x, theta[i], lambda[i], eta[i]), add=TRUE, 
        col=col[2], n=1000)
}
legend("topright", legend=labels, lty=1, col=col, seg.len=1)
par(opar)
@

<<dens_igaussian_marginalbeta, fig.cap="Marginal $p(\\beta_j)$ prior for several choices of $p(\\gamma^2_j)$ scaled to $\\V(\\beta_j)=1$.", out.width="60%", fig.asp=1>>=
library(GeneralizedHyperbolic)
# all scaled such that variance is one
sigma <- 1
theta <- 1/sigma^2
lambda <- c(0.1, 2)
lambda1 <- sqrt(2)
col <- c(1:4)
lty <- c(1:4)
labels <- as.expression(c(bquote("IG, "~lambda==.(lambda[1])~", "~
                                   theta==.(theta)),
                          bquote("IG, "~lambda==.(lambda[2])~", "~
                                   theta==.(theta)),
                          "Point mass (ridge)", "Exponential (lasso)"))
dprior <- function(x, lambda, theta, sigma) {
  dnig(x, 0, sigma*sqrt(lambda), sqrt(lambda/(theta*sigma)), 0)
}
dlasso <- function(x, lambda1) {
  0.5*lambda1*exp(-lambda1*abs(x))
}

curve(dprior(x, lambda[1], theta, sigma), -3, 3, ylab="Density", n=1000, 
      col=col[1], lty=lty[1])
curve(dprior(x, lambda[2], theta, sigma), add=TRUE, n=1000, 
      col=col[2], lty=lty[2])
curve(dnorm(x, 0, 1), add=TRUE, n=1000, col=col[3], lty=lty[3])
curve(dlasso(x, lambda1), add=TRUE, n=1000, col=col[4], lty=lty[4])
legend("topright", legend=labels, col=col, lty=lty)
@
